### 2020-03-11 article_draft.tex

\section{proposed testing procedure}
\label{sec:prop_test_proc}
For some test statistic $\tst$, any test of $H_0 : \disto \in \mathscr{M}_0$ versus $H_1 : \disto \not\in \mathscr{M}_0$ can be characterized by an acceptance region $\Theta_0(\disto) \subset \mathbb{R}^d$. This region $\Theta_0(\disto)$ can be chosen so the probability of rejection under the null is controlled asymptotically:
\begin{align}
  PR_{\distv}\{\rvv \not \in \Theta_0(p)\} = 1 - \alpha \text{ for every } P_0 \in \mathscr{M}_0 \text{ where } \tst \xrightarrow{P_0} \rvv \sim \distv(\disto).\label{eqn:alpha_rej}
\end{align}
While there are infinitely many regions satisfying \eqref{eqn:alpha_rej},  we focus for now on a particular class of regions defined using $\ell_p$ norms which will naturally lead to a straightforward testing procedure. For simplicity, first consider regions defined using an $\ell_2$ norm:
\begin{align}
	\Theta_0(r) = \left\{\omega : \|\omega\|_2 \leq r\right\}. \label{eqn:region}
\end{align}
a region satisfying \eqref{eqn:alpha_rej} and \eqref{eqn:region} has a radius defined by: 
% \textcolor{blue}{be consistent on indexing ``$pr$'' -- if you're going to write as $pr_{q(p)}$, do this throughout!}
\begin{align*}
	r_\alpha(\disto) = \min\left\{r : Pr_{\distv}(\|\rvv\|_2 \leq r) \geq 1 - \alpha \right\}.
\end{align*}
By constraining the possible regions we consider, we can now define our test.  Let $\hat{\boldsymbol{\Psi}} : \mathbb{R}^d \to \mathbb{R}$ be an estimator of $\boldsymbol{\psi}$, and let $\Hat{\boldsymbol{\psi}} \equiv \hat{\boldsymbol{\Psi}}(x)$ be an estimate of $\boldsymbol{\psi}$. Suppose for now that $\sqrt{n}\hat{\boldsymbol{\psi}}$ converges in law to a normal distribution $\distv(P)$ when $P$ is contained in the model space  $\mathcal{M}_0$.  Our test can be defined by 
\begin{align}
\label{eqn:simp_test}
	\text{reject } H_0 \text{ if } \|\sqrt{n} \hat{\boldsymbol{\psi}}\|_2 \geq r_\alpha,
\end{align} and p-values can now be defined by 
\begin{align}
	\text{Pr}_\distv(\|\rvv\|_2 \geq \|\sqrt{n} \hat{\boldsymbol{\psi}}\|_2)
\end{align}.

@@

The test defined in \eqref{eqn:simp_test} is a function of three objects. The first was the chosen norm.  The second was $\sqrt{n}\hat{\boldsymbol{\psi}}$.  The third was the limiting distribution of $\hat{t} = \sqrt{n}\hat{\boldsymbol{\psi}}$.  Note that the limiting distribution of $\hat{t}$ under the null will always be a multivariate normal with mean zero with some covariance $\Sigma$. Thus potential tests can be defined using the finite dimensional $\Sigma$ matrix rather than the infinite dimension distribution $Q(P)$.  Choosing the $\ell_2$ norm, we can define our test by:

>>>>

\section{Proposed Testing Procedure}
\label{sec:prop_test_proc}
For some test statistic $\tst$, any test of $H_0 : \disto \in \mathscr{M}_0$ versus $H_1 : \disto \not\in \mathscr{M}_0$ can be characterized by an acceptance region $\Theta_0(\disto) \subset \mathbb{R}^d$.  \textcolor{blue}{Let $ \tst \xrightarrow{P_0} \rvv \sim \distv(\disto)$}. This region $\Theta_0(\disto)$ can be chosen so the probability of rejection under the null is controlled asymptotically:
\begin{align}
  Pr_{\distv}\{\rvv \not \in \Theta_0(p)\} = 1 - \alpha \text{ for every } P_0 \in \mathscr{M}_0.\label{eqn:alpha_rej}
\end{align}
While there are many regions satisfying \eqref{eqn:alpha_rej},  we focus for now on a particular class of regions defined using $\ell_p$ norms which will naturally lead to a straightforward testing procedure. For simplicity, \textcolor{blue}{we} first consider regions defined using an $\ell_2$ norm:
\begin{align}
	\Theta_0(r) = \left\{\omega : \|\omega\|_2 \leq r\right\}. \label{eqn:region}
\end{align}
A region satisfying \eqref{eqn:alpha_rej} and \eqref{eqn:region} has a radius defined by: 
% \textcolor{blue}{be consistent on indexing ``$pr$'' -- if you're going to write as $pr_{q(p)}$, do this throughout!}
\begin{align*}
	r_\alpha(\disto) = \min\left\{r : Pr_{\distv}(\|\rvv\|_2 \leq r) \geq 1 - \alpha \right\}.
\end{align*}
We now construct a test using the region defined above.  Let $\hat{\boldsymbol{\Psi}} : \mathbb{R}^d \to \mathbb{R}$ be an estimator of $\boldsymbol{\psi}$, and let $\Hat{\boldsymbol{\psi}} \equiv \hat{\boldsymbol{\Psi}}(x)$ be an estimate of $\boldsymbol{\psi}$. Suppose for now that $\sqrt{n}\hat{\boldsymbol{\psi}}$ converges in law to a normal distribution $\distv(P)$ when $P$ is contained in the model space  $\mathcal{M}_0$.  Our test can be defined by 
\begin{align}
\label{eqn:simp_test}
	\text{reject } H_0 \text{ if } \|\sqrt{n} \hat{\boldsymbol{\psi}}\|_2 \geq r_\alpha,
\end{align} and the corresponding p-values are defined by $
	\text{Pr}_\distv(\|\rvv\|_2 \geq \|\sqrt{n} \hat{\boldsymbol{\psi}}\|_2)$.

@@

We can vary any of these three things to give us another test=
The test defined in \eqref{eqn:simp_test} depends on three objects. The first was the chosen norm.  The second was $\sqrt{n}\hat{\boldsymbol{\psi}}$.  The third was the limiting distribution of $\sqrt{n}\hat{\boldsymbol{\psi}}$.  To simplify this test, replace  $\sqrt{n}\hat{\boldsymbol{\psi}}$ with $ \tst \equiv \sqrt{n}\Sigma^{-1/2}\hat{\boldsymbol{\psi}}$. Because $\tst$ will always converge to a standard multivariate normal regardless of which $P \in \mathscr{M}_0$ is true \textcolor{blue}{(point to proof)}, for the test defined using $\tst$:
